Manuscript_Outputs

### 2024-01-24 Scripts/Stats_Analysis/RMarkdown/ManuscriptOutputs.Rmd
Swap AUC to Harrell's C

dt <- data.frame(model=c("Tyrer-Cuzick", "Model only", "Model with PRS", 
                         "Gail", "Model only", "Model with PRS"),
                 AUC=c(NA,
                       AUC_CI(df=test_data, score="TC_10risk_cal", status = "TEU_BrCa_status", dp=2),
                       AUC_CI(df=test_data, score="TC_prs_10risk", status = "TEU_BrCa_status", dp=2),
                       NA,
                       AUC_CI(df=test_data, score="gail_10risk_cal", status = "TEU_BrCa_status", dp=2),
                       AUC_CI(df=test_data, score="gail_prs_10risk", status = "TEU_BrCa_status", dp=2)),
                 NRI_overall=c(NA, nri_ci(nri_tc, type="overall", dp=3), nri_ci(nri_tc, type="overall", dp=3), 
                               NA, nri_ci(nri_gail, type="overall", dp=3), nri_ci(nri_gail, type="overall", dp=3)),
                 NRI_case=c(NA, nri_ci(nri_tc, type="case", dp=3), nri_ci(nri_tc, type="case", dp=3), 
                               NA, nri_ci(nri_gail, type="case", dp=3), nri_ci(nri_gail, type="case", dp=3)),
                 NRI_control=c(NA, nri_ci(nri_tc, type="control", dp=3), nri_ci(nri_tc, type="control", dp=3), 
                               NA, nri_ci(nri_gail, type="control", dp=3), nri_ci(nri_gail, type="control", dp=3)))

ft <- flextable(dt) %>%
  merge_v(j = ~ model + NRI_overall + NRI_case + NRI_control) %>%
  # separate_header(sep="_") %>%
  set_header_labels(model="Model", AUC="AUC (95% CI)",
                    NRI_overall="Overall", 
                    NRI_case=paste0("Case (N=", nrow(test_data[test_data$TEU_BrCa_time <= 10 &
                                                                 test_data$TEU_BrCa_status==1,]), ")"), 
                    NRI_control=paste0("Control (N=", nrow(test_data[test_data$TEU_BrCa_time > 10,]), ")")) %>%
  add_header_row(values=c("", "NRI"), colwidths=c(2, 3)) %>%
  align(align = "center", part = "all", j=c('AUC', 'NRI_overall', 'NRI_case', 'NRI_control')) %>%
  bg(i= ~ is.na(AUC), bg="lightgrey", part="body") %>%
  merge_at(i=1, j=1:5) %>%
  merge_at(i=4, j=1:5) %>%
  fix_border_issues(part="all") %>%
  set_table_properties(layout="autofit") %>%
  footnote(i=1, j=3, 
           value=as_paragraph("NRI: Net Reclassification Index for 10yr risks from model with PRS compared to Calibrated model, with a fixed proportion of women classified as high risk"), 
           ref_symbols="a", part="header") %>%
  footnote(i=2, j=3, 
           value=as_paragraph("Overall NRI = Case NRI + Control NRI, where cases are defined as individuals diagnosed with breast cancer within 10 years and controls are defined as individuals who were still at risk of breast cancer by 10 years of follow-up."), 
           ref_symbols="b", part="header")

@@

dt <- data.frame(model=c("Tyrer-Cuzick", "Model only", "Model with PRS", "Integrated PRS",
                         "Gail", "Model only", "Model with PRS"),
                 AUC=c(NA,
                       AUC_CI(df=test_data, score="TC_10risk_cal", status = "TEU_BrCa_status", dp=2),
                       AUC_CI(df=test_data, score="TC_prs313_10risk", status = "TEU_BrCa_status", dp=2),
                       AUC_CI(df=test_data, score="TC_10risk_Mavaddat2019_cal", status = "TEU_BrCa_status", dp=2),
                       NA,
                       AUC_CI(df=test_data, score="gail_10risk_cal", status = "TEU_BrCa_status", dp=2),
                       AUC_CI(df=test_data, score="gail_prs313_10risk", status = "TEU_BrCa_status", dp=2)),
                 NRI_overall=c(NA, NA, nri_ci(nri_tc, type="overall", dp=3), nri_ci(nri_tc_mav, type="overall", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="overall", dp=3)),
                 NRI_case=c(NA, NA, nri_ci(nri_tc, type="case", dp=3), nri_ci(nri_tc_mav, type="case", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="case", dp=3)),
                 NRI_control=c(NA, NA, nri_ci(nri_tc, type="control", dp=3), nri_ci(nri_tc_mav, type="control", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="control", dp=3)))

ft <- flextable(dt) %>%
  # merge_v(j = ~ model + NRI_overall + NRI_case + NRI_control) %>%
  # separate_header(sep="_") %>%
  set_header_labels(model="Model", AUC="AUC (95% CI)",
                    NRI_overall="Overall", 
                    NRI_case=paste0("Case (N=", nrow(test_data[test_data$TEU_BrCa_time <= 10 &
                                                                 test_data$TEU_BrCa_status==1,]), ")"), 
                    NRI_control=paste0("Control (N=", nrow(test_data[test_data$TEU_BrCa_time > 10,]), ")")) %>%
  add_header_row(values=c("", "NRI"), colwidths=c(2, 3)) %>%
  align(align = "center", part = "all", j=c('AUC', 'NRI_overall', 'NRI_case', 'NRI_control')) %>%
  bg(i= ~ is.na(AUC), bg="lightgrey", part="body") %>%
  merge_at(i=1, j=1:5) %>%
  merge_at(i=5, j=1:5) %>%
  fix_border_issues(part="all") %>%
  set_table_properties(layout="autofit") %>%
  footnote(i=1, j=3, 
           value=as_paragraph("NRI: Net Reclassification Index for 10yr risks from model with PRS compared to Calibrated model, with a fixed proportion of women classified as high risk"), 
           ref_symbols="a", part="header") %>%
  footnote(i=2, j=3, 
           value=as_paragraph("Overall NRI = Case NRI + Control NRI, where cases are defined as individuals diagnosed with breast cancer within 10 years and controls are defined as individuals who were still at risk of breast cancer by 10 years of follow-up."), 
           ref_symbols="b", part="header") %>%
  footnote(i=6, j=1, 
           value=as_paragraph("Integrated PRS is the output from the Tyrer-Cuzick model run with the PRS as an input, formatted as a log(OR)"), 
           ref_symbols="c", part="body")

>>>>

dt <- data.frame(model=c("Tyrer-Cuzick", "Model only", "Model with PRS", 
                         "Gail", "Model only", "Model with PRS"),
                 HarrellC=c(NA,
                       HarrellC_CI(df=test_data, score="TC_10risk_cal", 
                                   time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       HarrellC_CI(df=test_data, score="TC_prs_10risk", 
                                   time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       NA,
                       HarrellC_CI(df=test_data, score="gail_10risk_cal", 
                                   time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       HarrellC_CI(df=test_data, score="gail_prs_10risk", 
                                   time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2)),
                 NRI_overall=c(NA, nri_ci(nri_tc, type="overall", dp=3), nri_ci(nri_tc, type="overall", dp=3), 
                               NA, nri_ci(nri_gail, type="overall", dp=3), nri_ci(nri_gail, type="overall", dp=3)),
                 NRI_case=c(NA, nri_ci(nri_tc, type="case", dp=3), nri_ci(nri_tc, type="case", dp=3), 
                               NA, nri_ci(nri_gail, type="case", dp=3), nri_ci(nri_gail, type="case", dp=3)),
                 NRI_control=c(NA, nri_ci(nri_tc, type="control", dp=3), nri_ci(nri_tc, type="control", dp=3), 
                               NA, nri_ci(nri_gail, type="control", dp=3), nri_ci(nri_gail, type="control", dp=3)))

ft <- flextable(dt) %>%
  merge_v(j = ~ model + NRI_overall + NRI_case + NRI_control) %>%
  # separate_header(sep="_") %>%
  set_header_labels(model="Model", HarrellC="Harrell's C (95% CI)",
                    NRI_overall="Overall", 
                    NRI_case=paste0("Case (N=", nrow(test_data[test_data$TEU_BrCa_time <= 10 &
                                                                 test_data$TEU_BrCa_status==1,]), ")"), 
                    NRI_control=paste0("Control (N=", nrow(test_data[test_data$TEU_BrCa_time > 10,]), ")")) %>%
  add_header_row(values=c("", "NRI"), colwidths=c(2, 3)) %>%
  align(align = "center", part = "all", j=c("HarrellC", 'NRI_overall', 'NRI_case', 'NRI_control')) %>%
  bg(i= ~ is.na(HarrellC), bg="lightgrey", part="body") %>%
  merge_at(i=1, j=1:5) %>%
  merge_at(i=4, j=1:5) %>%
  fix_border_issues(part="all") %>%
  set_table_properties(layout="autofit") %>%
  footnote(i=1, j=3, 
           value=as_paragraph("NRI: Net Reclassification Index for 10yr risks from model with PRS compared to Calibrated model, with a fixed proportion of women classified as high risk"), 
           ref_symbols="a", part="header") %>%
  footnote(i=2, j=3, 
           value=as_paragraph("Overall NRI = Case NRI + Control NRI, where cases are defined as individuals diagnosed with breast cancer within 10 years and controls are defined as individuals who were still at risk of breast cancer by 10 years of follow-up."), 
           ref_symbols="b", part="header")

@@

dt <- data.frame(model=c("Tyrer-Cuzick", "Model only", "Model with PRS", "Integrated PRS",
                         "Gail", "Model only", "Model with PRS"),
                 HarrellC=c(NA,
                       HarrellC_CI(df=test_data, score="TC_10risk_cal", 
                              time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       HarrellC_CI(df=test_data, score="TC_prs313_10risk", 
                              time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       HarrellC_CI(df=test_data, score="TC_10risk_Mavaddat2019_cal", 
                              time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       NA,
                       HarrellC_CI(df=test_data, score="gail_10risk_cal", 
                              time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2),
                       HarrellC_CI(df=test_data, score="gail_prs313_10risk", 
                              time="TEU_BrCa_time", status = "TEU_BrCa_status", dp=2)),
                 NRI_overall=c(NA, NA, nri_ci(nri_tc, type="overall", dp=3), nri_ci(nri_tc_mav, type="overall", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="overall", dp=3)),
                 NRI_case=c(NA, NA, nri_ci(nri_tc, type="case", dp=3), nri_ci(nri_tc_mav, type="case", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="case", dp=3)),
                 NRI_control=c(NA, NA, nri_ci(nri_tc, type="control", dp=3), nri_ci(nri_tc_mav, type="control", dp=3), 
                               NA, NA, nri_ci(nri_gail, type="control", dp=3)))

ft <- flextable(dt) %>%
  # merge_v(j = ~ model + NRI_overall + NRI_case + NRI_control) %>%
  # separate_header(sep="_") %>%
  set_header_labels(model="Model", HarrellC="Harrell's C (95% CI)",
                    NRI_overall="Overall", 
                    NRI_case=paste0("Case (N=", nrow(test_data[test_data$TEU_BrCa_time <= 10 &
                                                                 test_data$TEU_BrCa_status==1,]), ")"), 
                    NRI_control=paste0("Control (N=", nrow(test_data[test_data$TEU_BrCa_time > 10,]), ")")) %>%
  add_header_row(values=c("", "NRI"), colwidths=c(2, 3)) %>%
  align(align = "center", part = "all", j=c("HarrellC", 'NRI_overall', 'NRI_case', 'NRI_control')) %>%
  bg(i= ~ is.na(HarrellC), bg="lightgrey", part="body") %>%
  merge_at(i=1, j=1:5) %>%
  merge_at(i=5, j=1:5) %>%
  fix_border_issues(part="all") %>%
  set_table_properties(layout="autofit") %>%
  footnote(i=1, j=3, 
           value=as_paragraph("NRI: Net Reclassification Index for 10yr risks from model with PRS compared to Calibrated model, with a fixed proportion of women classified as high risk"), 
           ref_symbols="a", part="header") %>%
  footnote(i=2, j=3, 
           value=as_paragraph("Overall NRI = Case NRI + Control NRI, where cases are defined as individuals diagnosed with breast cancer within 10 years and controls are defined as individuals who were still at risk of breast cancer by 10 years of follow-up."), 
           ref_symbols="b", part="header") %>%
  footnote(i=6, j=1, 
           value=as_paragraph("Integrated PRS is the output from the Tyrer-Cuzick model run with the PRS as an input, formatted as a log(OR)"), 
           ref_symbols="c", part="body")
